\cvsection{Experience}
\begin{cventries}
  \cventry
    {Summer Research Intern}
    {Siemens Technology and Services Pvt. Ltd.}
    {Bengaluru, India}
    {May, 2016 - July, 2016}
    {
      \begin{cvitems}
        \item {Developed APIs for parsing documents to extract useful information and creating first-order logic systems for generation of knowledge-based engineering systems.}
        \item {Created a surrogate model generator that implements an improved version of multivariate polynomial regression.}
      \end{cvitems}
    }
  \cventry
    {Full Stack Developer}
    {CybrHome}
    {Mangalore, India}
    {February, 2016 - March, 2016}
    {
      \begin{cvitems}
        \item {Worked on the development of the CybrHome chrome extension which can be used for discovering websites directly from the browser.}
      \end{cvitems}
    }
  \cventry
    {Summer Intern}
    {Foodbingo, IIT Bombay}
    {Mumbai, India}
    {May, 2015 - July, 2015}
    {
      \begin{cvitems}
        \item {Foodbingo was a startup incubated at IIT Bombay.}
        \item {Developed an application in JavaScript and GMaps v3 API. Additional responsibilities were working with front end technologies like Bootstrap and jQuery UI and DNS management.}
      \end{cvitems}
    }
  \cventry
    {Web Developer and Graphic Designer}
    {Youth Youniverse}
    {Work from Home}
    {March, 2015 - May, 2015}
    {
      \begin{cvitems}
        \item {Created the website for Youth Youniverse using Bootstrap v3, jQuery and PHP for the backend.}
        \item {Created graphics, posters and designs for various events GIMusing P.}
      \end{cvitems}
    }
\end{cventries}
